How many atlases do you really need for accurate multi-atlas segmentation?

### 2016-05-26 paper.Rnw
Clean up of the Rnw source

\begin{document}
\SweaveOpts{concordance=TRUE}
\maketitle

@@

\begin{figure}[t]
%\begin{minipage}[b]{1.0\linewidth}
  \centering
  %\includegraphics[width=\textwidth]{results}
<<performance, fig=TRUE, cached=TRUE, echo=FALSE, warnings=FALSE >>=
library(ggplot2)
results = read.csv(file='data/results.csv')
#results = read.csv(file='data/results_with_9multiatlas.csv')
xcorr_vote= subset(results, method=='xcorr' | method == 'multiatlas_xcorr_vote' )
qplot(x=top_n, y=k_hippocampus, data=xcorr_vote, colour=as.factor(num_atlases), geom=c('point'), alpha=I(0)) +
  geom_smooth(method='loess')+ #line=1.5, formula=y~poly(x,2), method='lm') + 
  geom_hline(aes(yintercept = mean(subset(results, method=='naive')$k_hippocampus), linetype="dashed")) + 
  theme(legend.position="none") + 
  ylab('Mean similarity score (Kappa)') + 
  xlab('Number of template labels fused') +
  annotate("text", 14.3, 0.712, label="Single-atlas", size=4, hjust=0)+
  annotate("text", 15.3, 0.754, label="3 atlases", size=4, hjust=0)+
  annotate("text", 14.4, 0.766, label="4 atlases", size=4, hjust=0)+
  annotate("text", 13.5, 0.770, label="5 atlases", size=4, hjust=0)+
  annotate("text", 12.5, 0.773, label="6 atlases", size=4, hjust=0)+
  annotate("text", 11.5, 0.776, label="7 atlases", size=4, hjust=0)+
  annotate("text", 10.3, 0.779, label="8 atlases", size=4, hjust=0)+
  annotate("text", 13.5, 0.793, label="Basic multi-atlas", size=4, hjust=0)+
  annotate("text", 14.6, 0.787, label="17 atlases", size=4, hjust=0)+
  scale_colour_manual(values=c(
    "#D73027","#FC8D59","#FEE08B","#D9EF8B", "#91CF60","#1A9850", "#000000")) + 
  scale_linetype_manual(values=c(
    "dotted", "solid", "solid", "solid",
         "solid", "solid", "solid", "dashed")) +
  coord_cartesian(ylim=c(0.703,0.803), xlim=c(3,18)) + scale_y_continuous(breaks=seq(0,1,0.01))   
@
%\end{minipage}
\caption{{\small
Mean performance of MAGeT brain with varying atlas library size and number of
template labels fused. Also shown is the mean basic multi-atlas
performance when using an atlas library of 17 images and varying the number of
labels fused, as well as the mean performance of single-atlas segmentations.
Data is fit with LOESS local regression smoothing. One standard deviation is
shown in grey.
}}
\label{results}
\end{figure}

>>>>

\begin{document}
\SweaveOpts{concordance=TRUE}

<<setup include=FALSE, echo=FALSE>>=
library(knitr)
opts_chunk$set(
concordance=TRUE
)
@

\maketitle

@@

\begin{figure}[t]
  \centering

<<performance, cached=TRUE, echo=FALSE, warnings=FALSE >>=
library(ggplot2)

results = read.csv(file='data/results.csv')
xcorr_vote= subset(results, method=='xcorr' | method == 'multiatlas_xcorr_vote' )

qplot(x=top_n, y=k_hippocampus, data=xcorr_vote, colour=as.factor(num_atlases), geom=c('point'), alpha=I(0)) +
  geom_smooth(method='loess')+ #line=1.5, formula=y~poly(x,2), method='lm') + 
  geom_hline(aes(yintercept = mean(subset(results, method=='naive')$k_hippocampus), linetype="dashed")) + 
  theme(legend.position="none") + 
  ylab('Mean similarity score (Kappa)') + 
  xlab('Number of template labels fused') +
  annotate("text", 14.3, 0.712, label="Single-atlas", size=4, hjust=0)+
  annotate("text", 15.3, 0.754, label="3 atlases", size=4, hjust=0)+
  annotate("text", 14.4, 0.766, label="4 atlases", size=4, hjust=0)+
  annotate("text", 13.5, 0.770, label="5 atlases", size=4, hjust=0)+
  annotate("text", 12.5, 0.773, label="6 atlases", size=4, hjust=0)+
  annotate("text", 11.5, 0.776, label="7 atlases", size=4, hjust=0)+
  annotate("text", 10.3, 0.779, label="8 atlases", size=4, hjust=0)+
  annotate("text", 13.5, 0.793, label="Basic multi-atlas", size=4, hjust=0)+
  annotate("text", 14.6, 0.787, label="17 atlases", size=4, hjust=0)+
  scale_colour_manual(values=c(
    "#D73027","#FC8D59","#FEE08B","#D9EF8B", "#91CF60","#1A9850", "#000000")) + 
  scale_linetype_manual(values=c(
    "dotted", "solid", "solid", "solid",
         "solid", "solid", "solid", "dashed")) +
  coord_cartesian(ylim=c(0.703,0.803), xlim=c(3,18)) + scale_y_continuous(breaks=seq(0,1,0.01))   
@
\caption{{\small
Mean performance of MAGeT brain with varying atlas library size and number of
template labels fused. Also shown is the mean basic multi-atlas
performance when using an atlas library of 17 images and varying the number of
labels fused, as well as the mean performance of single-atlas segmentations.
Data is fit with LOESS local regression smoothing. One standard deviation is
shown in grey.
}}
\label{results}
\end{figure}
